### 2020-12-03 README.Rmd
Update README

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-", 
  out.width = "90%",
  fig.width= 12,
  fig.height=3)
```
# robvis <img src="man/figures/robvis_hex_box.png" align="right" width="18%" height="18%" />

@@

#### 1. rob_summary()
Returns a ggplot object displaying a weighted barchart of the risk of bias of included studies across the domains of the specified tool.

```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")
summary_rob
```

@@

```{r, eval=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2,
                                      tool = "ROB2",
                                      psize = 10)
trafficlight_rob
```

``` {r, include=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2,
                                      tool = "ROB2",
                                      psize = 10)
rob_save(trafficlight_rob,"man/figures/rob2trafficlight.png")
```
<div style="text-align:center"><img src="man/figures/rob2trafficlight.png" width="70%" height="70%"/></div>

@@

```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2,
                           tool = "ROB2",
                           colour = "colourblind")
summary_rob
```

And to define your own colour scheme:
```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2,
                           tool = "ROB2",
                           colour = c("#f442c8",
                                      "#bef441",
                                      "#000000",
                                      "#d16684"))
summary_rob
```

### Created an unweighted summary barplot
By default, the `rob_summary()` function creates a barplot weighted by some measure of a study's precision. This can be prevented using the "weighted" argument. For example, compare the following two plots:

```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")
summary_rob
```

```{r, fig.height=3}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", weighted = FALSE)
summary_rob
```

@@

For example, to add a title to the unweighted RoB2.0 plot created above:
```{r warning=FALSE, fig.height=3}
library(ggplot2)

summary_rob +
  ggtitle("Summary of RoB2.0 assessments")
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-", 
  out.width = "90%",
  fig.width= 12,
  fig.height=3)

fig_count <- 1
```
# robvis <img src="man/figures/robvis_hex_box.png" align="right" width="18%" height="18%" />

@@

#### 1. rob_summary()
Returns a ggplot object displaying a barchart of the risk of bias of included studies across the domains of the specified tool. [*Note: the defaults used in this function have changed from their original settings, so that a un-weighted barplot is now produced by default. See the NEWS.md file for further information.*]

```{r, eval = FALSE}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2")

summary_rob
```

``` {r, echo = FALSE}
plot <- rob_summary(data = data_rob2, tool = "ROB2")
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

@@

```{r, eval=FALSE}
trafficlight_rob <- rob_traffic_light(data = data_rob2,
                                      tool = "ROB2",
                                      psize = 10)

trafficlight_rob
```

``` {r, echo = FALSE}
plot <- rob_traffic_light(data = data_rob2,
                  tool = "ROB2",
                  psize = 10)
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

@@

```{r, eval=FALSE}
rob_summary(data = data_rob2,
            tool = "ROB2",
            colour = "colourblind")

```

``` {r, echo = FALSE}
plot <- rob_summary(data = data_rob2,
                           tool = "ROB2",
                           colour = "colourblind")
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

And to define your own colour scheme:
```{r, eval=FALSE}
rob_summary(
  data = data_rob2,
  tool = "ROB2",
  colour = c("#f442c8",
             "#bef441",
             "#000000",
             "#d16684")
)

```

``` {r, echo = FALSE}
plot <- rob_summary(data = data_rob2,
                           tool = "ROB2",
                           colour = c("#f442c8",
                                      "#bef441",
                                      "#000000",
                                      "#d16684"))
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

### No "Overall" judgement

By default, both functions include an "Overall" risk of bias domain. To prevent this, set `overall = FALSE`.

```{r, eval=FALSE}
summary_rob <- rob_summary(data = data_rob2, tool = "ROB2", overall = FALSE)
summary_rob
```

``` {r, echo = FALSE}
plot <- rob_summary(data = data_rob2,
                           tool = "ROB2",
                           colour = c("#f442c8",
                                      "#bef441",
                                      "#000000",
                                      "#d16684"))
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

```{r, eval=FALSE}
rob_traffic_light(data = data_rob2,
                  tool = "ROB2",
                  overall = FALSE)
```

``` {r, echo = FALSE}
plot <- rob_traffic_light(data = data_rob2,
                                      tool = "ROB2",
                                      overall = FALSE)
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>

@@

For example, to add a title:
```{r, eval=FALSE}
library(ggplot2)

rob_summary(data = data_rob2, tool = "ROB2") +
  ggtitle("Summary of RoB 2.0 assessments")
```

``` {r, echo = FALSE}
plot <- rob_summary(data = data_rob2, tool = "ROB2") +
  ggplot2::ggtitle("Summary of RoB2.0 assessments")
file = paste0("man/figures/robplot",fig_count,".png")
rob_save(plot, file)
fig_count <- fig_count + 1
```
<div style="text-align:center"><img src=`r file` width="70%" height="70%"/></div>
